A Grimm idea

### 2016-05-06 presentation/main.tex
barrier construction tikzed
small correction

\begin{frame}
  \frametitle{Brobdignagian graphs}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Indistinguishable vertices
      \item Bounded degree ($\Delta$)
      \item Edges can locally enumerated $\left\{0,\dots,\Delta-1\right\}$
        (Port)
      \item Agent is aware of:
        \begin{enumerate}
          \item Degree  of vertex
          \item Pebbles placed on vertex
          \item Pebbles carried by agent
          \item Port    agent entered vertex
        \end{enumerate}
    \end{itemize}
    \column{0.5\textwidth}
    \begin{center}
      % \resizebox{\textwidth}{!}{\input{tikz/portex}}
    \end{center}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Exploration sequence}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Describe movement of agent by relative turns
      \item $e_{1},\dots, e_{n}$
      \item For a vertex $v$ with degree $d_{v}$ which is entered on port $p$
        is left through port $p + e_{i}\mod p$
      \item<2->[$\rightarrow$] Example:
        $\alt<3-3>{\colorbox{green}{1}}{\colorbox{white!0}{1}},
        \alt<4-4>{\colorbox{green}{3}}{\colorbox{white!0}{3}},
        \alt<5-5>{\colorbox{green}{2}}{\colorbox{white!0}{2}},
        \alt<6-6>{\colorbox{green}{2}}{\colorbox{white!0}{2}}$
    \end{itemize}
    \column{0.5\textwidth}
    \begin{center}
      % \resizebox{\textwidth}{!}{\input{tikz/moveex}}
    \end{center}
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{Exploring pebble machine}
  \alt<+>{
    \begin{theorem}[Reingold]
      There is an algorithm $A$ with $\mathcal{O}(n)$ space requirement
      producing a universal exploration sequence for every regular graph with
      $n$ vertices.
    \end{theorem}
  }{
    \begin{theorem}
      Thus, there is $(\mathcal{O}(1), 0, \mathcal{O}(\log n))$ that moves
      along a closed walk with $n$ distinct vertices (or explores the whole
      graph).
    \end{theorem}
  }
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item<3-> Establish 3-regularity
        \begin{itemize}
          \item Transform $v$ to $3\cdot d_{v}$ distinct vertices
          \item TODO: ADD BOUNDARY
        \end{itemize}
      \item<5-> Use $A$ and take first $k = 3n\cdot c$ ($c$ number of
        configurations $M_{A}$)
    \end{itemize}
    \column{0.5\textwidth}
    % \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
  \end{columns}
\end{frame}

\section{Simulation}
\begin{frame}
  \frametitle{Tape simulation via pebbles}
  \begin{itemize}
    \item Simulate tape of size $m$ by pebbles:
      \begin{itemize}
        \item<3-> Separate into memory blocks of size $m_{1}$
        \item<4-> Represent every block by one of $\left\{p_{0},\dots,p_{\frac{m}{m_{1}-1}}\right\}$ pebbles
      \end{itemize}
  \end{itemize}
  % \uncover<2->{\input{tikz/tapesimint}}
\end{frame}

\begin{frame}
  \frametitle{Tape simulation via pebbles}
  % \input{tikz/tapesimpebsep}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Every pebbles needs $2^{m_{1}}$ distinct \enquote{states}
        \begin{itemize}
          \item Placement on a walk with at least $2^{m_{1}}$ distinct vertices
            yields \enquote{states}
        \end{itemize}
    \end{itemize}
    \column{0.5\textwidth}
    % \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{Finding distinct vertices}
  Problem: Indistinguishable vertices $\leadsto$ next vertex \enquote{new}?
  \begin{columns}
    \column{0.5\textwidth}
    Solution:
    \begin{enumerate}
      \item Execute step
      \item Drop pebble $p_{\text{tmp}}$
      \item Store $\Twalk$ in $T'_{\text{walk}}$
      \item Restart $M_{\text{Walk}}$
      \item Execute steps until $p_{\text{tmp}}$ is observed
      \item If $\Twalk = T'_{\text{walk}}$ the vertex is new
      \item Otherwise start over
    \end{enumerate}
    \column{0.5\textwidth}
    % \input{tikz/disvert}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Memory management}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item $\Thead$ stores head position
      \item $p_{\lfloor\frac{\Thead}{m_{1}}\rfloor}$: pebble of memory block
      \item $\mathit{off} = \Thead\mod m_{1}$: offset in memory block
      \item Reading:
        \begin{itemize}
          \item Retrieve encoding pebble
          \item Return bit with offset
        \end{itemize}
      \item Writing:
        \begin{itemize}
          \item Read bit
          \item On bit-flip move encoding pebble $2^{\mathit{off}}$ bits up or down
        \end{itemize}
    \end{itemize}
    \column{0.5\textwidth}
    % \resizebox{\textwidth}{!}{\input{tikz/tapesimpebsep}}
    % \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Memory management: Writing}
  \begin{itemize}
    \item Read bit
    \item On bit-flip: move pebble
  \end{itemize}
  % \resizebox{\textwidth}{!}{\input{tikz/bitwrite}}
\end{frame}

@@

\begin{frame}
  \frametitle{Barrier construction: The real deal}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item $B$ has no pebbles and is therefore prone to a $0$-barrier
    \end{itemize}
    \column{0.5\textwidth}
  \end{columns}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Brobdignagian graphs}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Indistinguishable vertices
      \item Bounded degree ($\Delta$)
      \item Edges can locally enumerated $\left\{0,\dots,\Delta-1\right\}$
        (Port)
      \item Agent is aware of:
        \begin{enumerate}
          \item Degree  of vertex
          \item Pebbles placed on vertex
          \item Pebbles carried by agent
          \item Port    agent entered vertex
        \end{enumerate}
    \end{itemize}
    \column{0.5\textwidth}
    \begin{center}
      \resizebox{\textwidth}{!}{\input{tikz/portex}}
    \end{center}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Exploration sequence}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Describe movement of agent by relative turns
      \item $e_{1},\dots, e_{n}$
      \item For a vertex $v$ with degree $d_{v}$ which is entered on port $p$
        is left through port $p + e_{i}\mod p$
      \item<2->[$\rightarrow$] Example:
        $\alt<3-3>{\colorbox{green}{1}}{\colorbox{white!0}{1}},
        \alt<4-4>{\colorbox{green}{3}}{\colorbox{white!0}{3}},
        \alt<5-5>{\colorbox{green}{2}}{\colorbox{white!0}{2}},
        \alt<6-6>{\colorbox{green}{2}}{\colorbox{white!0}{2}}$
    \end{itemize}
    \column{0.5\textwidth}
    \begin{center}
      \resizebox{\textwidth}{!}{\input{tikz/moveex}}
    \end{center}
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{Exploring pebble machine}
  \alt<+>{
    \begin{theorem}[Reingold]
      There is an algorithm $A$ with $\mathcal{O}(n)$ space requirement
      producing a universal exploration sequence for every regular graph with
      $n$ vertices.
    \end{theorem}
  }{
    \begin{theorem}
      Thus, there is $(\mathcal{O}(1), 0, \mathcal{O}(\log n))$ that moves
      along a closed walk with $n$ distinct vertices (or explores the whole
      graph).
    \end{theorem}
  }
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item<3-> Establish 3-regularity
        \begin{itemize}
          \item Transform $v$ to $3\cdot d_{v}$ distinct vertices
          \item TODO: ADD BOUNDARY
        \end{itemize}
      \item<5-> Use $A$ and take first $k = 3n\cdot c$ ($c$ number of
        configurations $M_{A}$)
    \end{itemize}
    \column{0.5\textwidth}
    \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
  \end{columns}
\end{frame}

\section{Simulation}
\begin{frame}
  \frametitle{Tape simulation via pebbles}
  \begin{itemize}
    \item Simulate tape of size $m$ by pebbles:
      \begin{itemize}
        \item<3-> Separate into memory blocks of size $m_{1}$
        \item<4-> Represent every block by one of $\left\{p_{0},\dots,p_{\frac{m}{m_{1}}-1}\right\}$ pebbles
      \end{itemize}
  \end{itemize}
  \uncover<2->{\input{tikz/tapesimint}}
\end{frame}

\begin{frame}
  \frametitle{Tape simulation via pebbles}
  \input{tikz/tapesimpebsep}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Every pebbles needs $2^{m_{1}}$ distinct \enquote{states}
        \begin{itemize}
          \item Placement on a walk with at least $2^{m_{1}}$ distinct vertices
            yields \enquote{states}
        \end{itemize}
    \end{itemize}
    \column{0.5\textwidth}
    \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{Finding distinct vertices}
  Problem: Indistinguishable vertices $\leadsto$ next vertex \enquote{new}?
  \begin{columns}
    \column{0.5\textwidth}
    Solution:
    \begin{enumerate}
      \item Execute step
      \item Drop pebble $p_{\text{tmp}}$
      \item Store $\Twalk$ in $T'_{\text{walk}}$
      \item Restart $M_{\text{Walk}}$
      \item Execute steps until $p_{\text{tmp}}$ is observed
      \item If $\Twalk = T'_{\text{walk}}$ the vertex is new
      \item Otherwise start over
    \end{enumerate}
    \column{0.5\textwidth}
    \input{tikz/disvert}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Memory management}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item $\Thead$ stores head position
      \item $p_{\lfloor\frac{\Thead}{m_{1}}\rfloor}$: pebble of memory block
      \item $\mathit{off} = \Thead\mod m_{1}$: offset in memory block
      \item Reading:
        \begin{itemize}
          \item Retrieve encoding pebble
          \item Return bit with offset
        \end{itemize}
      \item Writing:
        \begin{itemize}
          \item Read bit
          \item On bit-flip move encoding pebble $2^{\mathit{off}}$ bits up or down
        \end{itemize}
    \end{itemize}
    \column{0.5\textwidth}
    \resizebox{\textwidth}{!}{\input{tikz/tapesimpebsep}}
    \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Memory management: Writing}
  \begin{itemize}
    \item Read bit
    \item On bit-flip: move pebble
  \end{itemize}
  \resizebox{\textwidth}{!}{\input{tikz/bitwrite}}
\end{frame}

@@

\begin{frame}
  \frametitle{Barrier construction: The real deal}
  \begin{itemize}
    \item $B$ has no pebbles and is therefore prone to a $0$-barrier
    \item Apply locality gadget to all edges
    \item This yields a $p$-barrier for the chosen subset of pebbles
    \item Iterate $p$-barriers for all possible subsets
  \end{itemize}
  \begin{center}
    \resizebox{0.8\textwidth}{!}{\input{tikz/iterbarrier}}
  \end{center}
\end{frame}
